Appendix

### 2020-04-01 manuscript/appendix.Rmd
use unlogged ag in scatterplot and percent tile drainage

fit_tn      <- lm(log(tn) ~ log(ag), data = dt)
fit_tn_pred <- data.frame(tn = fit_tn$model$`log(tn)`,
                          tn_pred = fit_tn$fitted.values,
                          ag = fit_tn$model$`log(ag)`,
                          stringsAsFactors = FALSE)
# ggplot(data = fit_tn_pred) + 
#   geom_point(aes(x = tn, y = tn_pred)) +
#   geom_abline(slope = 1)
# 
fit_tp      <- lm(log(tp) ~ log(ag), data = dt)
fit_tp_pred <- data.frame(tp = fit_tp$model$`log(tp)`,
                          tp_pred = fit_tp$fitted.values,
                          ag = fit_tp$model$`log(ag)`,
                          stringsAsFactors = FALSE)
# ggplot(data = fit_tp_pred) + 
#   geom_point(aes(x = tp, y = tp_pred)) +
#   geom_abline(slope = 1)

@@

cowplot::plot_grid(
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tn)) + 
  geom_line(data = fit_tn_pred, aes(x = exp(ag), y = exp(tn_pred)), 
             color = "red") +
  annotate("text", x = 14, y = 12000, label = get_formula("log(tn)", fit_tn), 
           size = 2) +
  ylab("TN (ug/L)") +
  xlab("Percent Agriculture") +
  scale_x_log10() + scale_y_log10() +
  theme_cowplot(), 
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tp)) + 
    geom_line(data = fit_tp_pred, aes(x = exp(ag), y = exp(tp_pred)), 
             color = "red") +
  annotate("text", x = 14, y = 900, label = get_formula("log(tp)", fit_tp), 
           size = 2) +
  ylab("TP (ug/L)") +
  xlab("Percent Agriculture") +
  scale_x_log10() + scale_y_log10() +
  theme_cowplot()
)

@@

```{r tile_drainage_vs_clay, fig.cap = "Scatterplot showing the median clay content of watersheds in our hydrologic regions plotted against percent tile drainage from Nakagaki and Wieczorek (2016). The regions that are highly sensitive to agriculture land-use from Figure 4 are highlighted.", warning=FALSE, echo = FALSE, eval=TRUE, fig.height=3, fig.width=3.3}
# load huc4 clay estimates
signif_hu4_ids <- c("HU4_56", "HU4_57")
dt <- readRDS("../data/dt.rds") %>%
  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
  dplyr::select(lagoslakeid, hu4_zoneid, clay_pct, signif_hu4) %>%
  group_by(hu4_zoneid) %>%
  mutate(median = median(clay_pct, na.rm = TRUE)) %>%
  distinct(hu4_zoneid, median, signif_hu4)

@@

# scatter plot clay versus tile drainage highlighting sensitve hucs
ggplot(data = test2) +
  geom_point(aes(x = tile_drainage/900, # grid cells are 30x30 = 900
                 y = median, color = signif_hu4)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  xlab("Percent tile drainage") + ylab("Median clay content (percent)") +
  cowplot::theme_cowplot() +
  theme(legend.position = c(0.6, 0.3), 
        legend.background = element_rect(fill = "white", color = "black"),
        legend.text = element_text(size = 10), 
        legend.title = element_text(size = 11)) +
  labs(color = "LULC Sensitive")
```

>>>>

fit_tn      <- lm(log(tn) ~ ag, data = dt)
fit_tn_pred <- data.frame(tn = fit_tn$model$`log(tn)`,
                          tn_pred = fit_tn$fitted.values,
                          ag = fit_tn$model$ag,
                          stringsAsFactors = FALSE)
# ggplot(data = fit_tn_pred) + 
#   geom_point(aes(x = tn, y = tn_pred)) +
#   geom_abline(slope = 1)
# 
fit_tp      <- lm(log(tp) ~ ag, data = dt)
fit_tp_pred <- data.frame(tp = fit_tp$model$`log(tp)`,
                          tp_pred = fit_tp$fitted.values,
                          ag = fit_tp$model$ag,
                          stringsAsFactors = FALSE)
# ggplot(data = fit_tp_pred) + 
#   geom_point(aes(x = tp, y = tp_pred)) +
#   geom_abline(slope = 1)

@@

cowplot::plot_grid(
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tn)) + 
  geom_line(data = fit_tn_pred, aes(x = ag, y = exp(tn_pred)), 
             color = "red") +
  annotate("text", x = 24, y = 12000, label = get_formula("log(tn)", fit_tn), 
           size = 2) +
  ylab("TN (ug/L)") +
  xlab("Percent Agriculture") +
  scale_y_log10() +
  theme_cowplot(), 
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tp)) + 
    geom_line(data = fit_tp_pred, aes(x = ag, y = exp(tp_pred)), 
             color = "red") +
  annotate("text", x = 24, y = 900, label = get_formula("log(tp)", fit_tp), 
           size = 2) +
  ylab("TP (ug/L)") +
  xlab("Percent Agriculture") +
  scale_y_log10() +
  theme_cowplot()
)

@@

```{r tile_drainage_vs_clay, fig.cap = "Scatterplot showing the median clay content of watersheds in our hydrologic regions plotted against percent tile drainage from Nakagaki and Wieczorek (2016). The regions that are highly sensitive to agricultural land-use from Figure 4 are highlighted in red.", warning=FALSE, echo = FALSE, eval=TRUE, fig.height=3, fig.width=3.3}
# load huc4 clay estimates
signif_hu4_ids <- c("HU4_56", "HU4_57")
dt <- readRDS("../data/dt.rds") %>%
  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
  dplyr::select(lagoslakeid, hu4_zoneid, clay_pct, signif_hu4) %>%
  group_by(hu4_zoneid) %>%
  mutate(median = median(clay_pct, na.rm = TRUE)) %>%
  distinct(hu4_zoneid, median, signif_hu4)

@@

# scatter plot clay versus tile drainage highlighting sensitve hucs
ggplot(data = test2) +
  geom_point(aes(x = (tile_drainage/900) * 100, # grid cells are 30x30 = 900
                 y = median, color = signif_hu4)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  xlab("Tile drainage (percent)") + ylab("Median clay content (percent)") +
  cowplot::theme_cowplot() +
  theme(legend.position = "none", 
        legend.background = element_rect(fill = "white", color = "black"),
        legend.text = element_text(size = 10), 
        legend.title = element_text(size = 11)) +
  labs(color = "LULC Sensitive")
```
